---
title: "Descriptive Statistics"
mainfont: DejaVu Sans
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
  html_document: default
  word_document: default
  font-family: Times New Roman
---


```{r}

library(tidyselect)
library(skimr)

```

```{r}

## library(skimr)

## # config
## skim_with(numeric = list(p0 = NULL, p25 = NULL, p75 = NULL, p100 = NULL, missing = NULL, complete = NULL))

## skim(pre_dist_multi_final[,-c(1, 16:ncol(pre_dist_multi_final))] %>% select(-respondents_quant))


```

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = 'asis'}

# config
skim_with(numeric = list(p0 = NULL, p25 = NULL, p75 = NULL, p100 = NULL, missing = NULL, complete = NULL))

skim(pre_dist_multi_final[,-c(1, 16:ncol(pre_dist_multi_final))] %>% select(-respondents_quant)) %>%
  kable(format = "latex", booktabs = T)

```


# Software Items

## Using information about the OS to cluster software items

### point

Generally, each software item transcends from the respondent. 

for each respondent might be calculate the number of:  
 - platforms used  
 - OS used  
 - OS used per platform  
aggregate this per software item using mean() and treating them equally.  

### couldn't be made

Only `df %>% filter(status == 1 & !is.na(Q85_1_1)) %>% nrow` respondents answered on questions which OS they use on different devices.


# Respondents  

## FIXME: due to the lots of NAs on Q85_* items, skip this and use Q4* items instead

```{r}

dfDiversity %>% filter(DesktopOsDiversity > 1) %>% nrow() # 49 respondents use more than one OS for desktop
dfDiversity %>% filter(LaptopOsDiversity > 1) %>% nrow() # 47 respondents use more than one OS for laptop
dfDiversity %>% filter(TabletOsDiversity > 1) %>% nrow() # 36 respondents use more than one OS for tablet
dfDiversity %>% filter(MobileOsDiversity > 1) %>% nrow() # 46 respondents use more than one OS for mobile

# Are they are the same respondents?

c(dfDiversity %>% filter(DesktopOsDiversity > 1) %$% RecordNo, dfDiversity %>% filter(LaptopOsDiversity > 1) %$% RecordNo,
  dfDiversity %>% filter(TabletOsDiversity > 1) %$% RecordNo, dfDiversity %>% filter(MobileOsDiversity > 1) %$% RecordNo) %>% unique() %>% length() # 81 respondents in total use more than 1 OS regarding all platforms



```

