---
title: "5_Using_Latent_Profiles_for_Software_Mapping"
mainfont: DejaVu Sans
output:
pdf_document:
latex_engine: xelatex
keep_tex: true
html_document: default
word_document: default
font-family: Times New Roman
---


```{r}


source('010_data_preprocessing.R')

library(tidyverse)
library(magrittr)
library(tidyLPA)

library(mclust)
library(forcats)
library(hrbrthemes)

library(knitr)
library(kableExtra)

library(graphics)
library(PMCMR)

library(gridExtra)

source("./functions.R")

```


```{r}


Q85_1_1_Q85_1_5
Q85_2_1_Q85_2_5
Q85_3_1_Q85_3_5
Q85_4_1_Q85_4_5


Q17 - employment status # intention to work
# df_clean$Q17 %>% summary()

df_clean$Q17_R = 6 - df_clean$Q17


Q18 - job title # use Occupation instead
df_clean$Q18 %>% summary()

df_clean$Occupation %>% unique()
# TODO: make occupations binary

## Occupation is binary 
## tmp = df_clean %>%
##   gather(key, val, Occupation) %>% 
##   dplyr::select(RecordNo, key, val) %>% 
##   group_by(RecordNo, val) %>% tally() %>%
##   spread(val, n, fill = 0)  %>%
##   ungroup()

# df_pre_lpa = inner_join(df_clean, tmp, by = "RecordNo")


# Q19 - private/public sector
df_clean$Q19[df_clean$Q19 == 1] = "Private"
df_clean$Q19[df_clean$Q19 == 2] = "Public"
df_clean$Q19[is.na(df_clean$Q19)] = "Not_Indicated"

# df_clean %>% apply(2, is.na)

#df_clean$Q19 %>% as.factor() %>% summary()


Q20 - industry
df_clean$Q20 %>% summary()
# TODO: Q20 - decrease number of level

# Q22 - not include, but check

df_clean$gender[df_clean$gender == 1] = "w"
df_clean$gender[df_clean$gender == 2] = "m"


df_clean$profile_age1

df_clean$region[df_clean$region == 1] = "Hovedstaden"
df_clean$region[df_clean$region == 2] = "Sjælland"
df_clean$region[df_clean$region == 3] = "Syddanmark"
df_clean$region[df_clean$region == 4] = "Midtjylland"
df_clean$region[df_clean$region == 5] = "Nordjylland"



# Education
df_clean$profile_education 
# df_clean$ed_not_indicated = ifelse(df_clean$profile_education == 9, 1, 0) # those, not indicated education might indicate lowest/highest levels of skill
df_clean$device_category # higher value - higher agency of device


df_final = df_clean %>% dplyr::select(RecordNo,
                                      ## Q85_1_1:Q85_4_5,
                                      Q17_R,
                                      Occupation,
                                      Q19,
                                      gender,
                                      region,
                                      profile_education,
                                      profile_age1,
                                      device_category)



```


# Statistical Testing Block

Here I am constructing simple variables like number of:  

 - unique software used  = n_unique_soft
 - unique software use per device  
 - software used out of the top-10 popular items  = n_unique_soft_non_pop
 - software use out of the top-10 popular per device = n_unique_soft_per_q_non_pop^[I used camelCase versions of the variables later - latex does not get well with "__" symbols].
 
 
I do not completely understand which theoretical constructs they do represent yet, but found them useful in testing differences between profiles later.


```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}

# TODO: move this calculations to the .R script to get rid of repetitions
# TODO: populate with other vars after spread
# vars1 =



software_cleaned  %>%
  group_by(RecordNo) %>%
  mutate(n_unique_soft = n()) %>%
  ungroup() %>%
  group_by(RecordNo, q) %>%
  mutate(n_unique_soft_per_q = n(), id = row_number()) %>% ungroup %>%
  spread(q, n_unique_soft_per_q) %>% 
  ungroup() %>% dplyr::select(-a, -q)

## Number of software used out of top-10

vars2 = software_cleaned  %>%
  filter(!(.$a2 %in% (software_aggregated %>% top_n(10, n) %$% a2))) %>% 
  group_by(RecordNo) %>%
  mutate(n_unique_soft_non_pop = n()) %>%
  ungroup() %>%
  group_by(RecordNo, q) %>%
  mutate(n_unique_soft_per_q_non_pop = n()) %>%
  ungroup() %>% dplyr::select(-a, -q)

tmp = inner_join(df_clean, vars2, by = "RecordNo")
tmp %>% nrow
tmp1 = inner_join(df_clean, vars1, by = "RecordNo")
tmp1 %>% nrow
tmp1 %>% View

#### Stat - Occupation/Profile

## m3 %>%
##   group_by(profile, Occupation) %>%
##   tally() %>%
##   dplyr::mutate(perc_per_profile = n / sum(n) * 100) %>%
##   ungroup() %>%
##   dplyr::mutate(perc_total = n / sum(n) * 100) %>% View



```



TODO: what I need to do is to consider public/private sector   
Q19 - do you work in a public/private sector   


```{r, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}

# Here I am excluding timing columns

df_clean %<>%
  dplyr::select(-c(page_pSC1_timing:tot_time))

# df_clean %>% nrow
na_vector = apply(df_clean, 2, function(x){

  sum(is.na(x))

})

na_vector[na_vector > 0] # which variables produce most of the NAs
## df_final = df_clean %>% dplyr::select(
##                                       names(na_vector[na_vector == 0]),
##                                       -Occupation_Num, -status, -Occupation_DISCO,
##                                       -c(Q85a_1_1, Q85a_2_1, Q85a_3_1, Q85a_4_1),
##                                       -c(Q21_1_open, Q22),
##                                       -c(Q18_1_open, Q18a),
##                                       -c(comments, Q4, Q5, Q6, Q7))

df_final %>% View



```



```{r, include=TRUE, warning=FALSE, message=FALSE, echo=FALSE}

## Reordering variables to make values semi-continuous

## df_final$Q9[df_final$Q9 == 4] = 0
## df_final$Q10[df_final$Q10 == 4] = 0
## df_final$Q11[df_final$Q11 == 4] = 0
## df_final$Q12[df_final$Q12 == 4] = 0
## df_final$Q13[df_final$Q13 == 4] = 0
## df_final$Q14[df_final$Q14 == 4] = 0
## df_final$Q15[df_final$Q15 == 4] = 0
## df_final$Q16[df_final$Q16 == 4] = 0

## df_final$Q17_R = 6 - df_final$Q17


```

## Description of items for LPA   


```{r, include=TRUE}


# df_clean$Q1 %>% as.factor() %>% summary() # only 16 indicated other than Dansk
# Q1 - language

# Q3_1 - Desktop
# Q3_2 - Laptop
# Q3_3 - Tablet
# Q3_4 - Mobile phone/Smartphone
#

# Q8_v2_1 - Built-in default settings
# Q8_v2_2 - Plugins/add-ons/extensions
# Q8_v2_3 - Script to extend Software
# Q8_v2_4 - I reprogram

# Traditional Surveys
# Q9 - Q10 - Q11 - Q12 - Q13 - Q14 - Q15 - Q16 - Q16

# Q17_R - employment status


```


Latent Profile Analysis is used in social science and educational research. It suits the needs to aggregate reprogrammability items, though, need to check how it will deal with Occupations and SES.


```{r, include=FALSE, message=FALSE, warning=FALSE, echo=FALSE}

# Q17 - employment status, using Reversed Ordered Q17_R instead

## vars_to_exclude = c("RecordNo", "weight","Q17",
##                     "Occupation", "profile_education",
##                     "profile_age2", "profile_age1",
##                     "region", "Q1", "gender")

d = df_final

## colnames_lpa = colnames(d)[!(colnames(d) %in% vars_to_exclude)]


```

Number of profiles to choose - analytically - **less BIC is better**.  

```{r, message=FALSE, warning=FALSE, echo=FALSE}

## fit_output = explore_model_fit(d %>% dplyr::select(colnames_lpa),
##                                n_profiles_range = 1:6)

# is.na(df_clean$Q85_1_1) %>% sum() 
df_clean %>% View

d %>% View
d %>% nrow()

apply(d, 2, FUN = is.na) %>% View

apply(d, 2, FUN = function(x) sum(is.na(x))) %>% View

ttt = d %>% dplyr::select(-Occupation, -region, -Q19)

ttt %>% View

fit_output = explore_model_fit(ttt,
                               n_profiles_range = 1:6)


fit_output %>% knitr::kable(digits = 2) %>% kable_styling(bootstrap_options = "striped", full_width = T) 

```

**Number of profiles to choose - visually**


Freed variance - variance might vary across the groups. Constrained variance means that profiles are chosen according to the assumption that variance should be closely the same in all of the profiles. Fixed variance indicates the strength of this assumption, so, variance is less then in case of Constrained Variance.   

In it's turn, covariance indicate the degree of variation for interconnection of variables across profiles. Basic example - income should be equally connected with education across all profiles in case of fixed covariance.   

Two models are plotted:

- Constrained variance, fixed covariance
- Constrained variance, constrained covariance (+)

Based on the BIC, we should choose EEE = Constrained variance, constrained covariance model = model 2.

```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}

to_plot = fit_output %>%
  gather(`Covariance matrix structure`, val, -n_profiles) %>% 
  mutate(`Covariance matrix structure` = as.factor(`Covariance matrix structure`),
         val = abs(val)) # this is to make the BIC values positive (to align with more common formula / interpretation of BIC)


to_plot$`Covariance matrix structure` = forcats::fct_relevel(to_plot$`Covariance matrix structure`,
                                                             "Constrained variance, fixed covariance",
                                                             "Freed variance, fixed covariance",
                                                             "Constrained variance, constrained covariance",
                                                             "Freed variance, freed covariance")

# Based on plot, either 3 or 4 profiles should be setted up

ggplot(data = to_plot,
       aes(x = n_profiles, y = val, color = `Covariance matrix structure`, group = `Covariance matrix structure`)) +
  geom_line() + geom_point() + ylab("BIC (smaller value is better)") # + theme_ipsum_rc()


```

Choosing the model with 5 profiles.

```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}

## SOLVED: exclude binary variables from LPA

m3 = estimate_profiles(d,
                       colnames_lpa,
                       n_profiles = 5, 
                       model = 2,
                       return_orig_df = T)


```


```{r, include=FALSE, message=FALSE, warning=FALSE, echo=FALSE}

## Plotting 
# RColorBrewer::brewer.pal(n, pal)
# https://www.r-bloggers.com/how-to-expand-color-palette-with-ggplot-and-rcolorbrewer/

## plot_profiles(m3[, !(colnames(m3) %in% vars_to_exclude)])


```

# Plotting   


```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.cap = "Reprogrammability Items Across Profiles: Will make a bit more sense later in conjunction with Occupations", dev='png', fig.width=14, fig.height=12}


## m3 = estimate_profiles(d,
##                        colnames_lpa,
##                        n_profiles = , 
##                        model = 2,
##                        return_orig_df = T)


q8_plot = plot_profiles(m3[, c("Q8_v2_1", "Q8_v2_2", "Q8_v2_3", "Q8_v2_4", "profile", "posterior_prob")])

q8_plot

## ggsave(device="png", plot=q8_plot, filename="./plots/q8_plot.png", scale=.2, height = 1024, width = 1024, units = "mm")


```
