---
title: "3_Network_Rerpresentation"
mainfont: DejaVu Sans
output:
pdf_document:
latex_engine: xelatex
keep_tex: true
html_document: default
word_document: default
font-family: Times New Roman
---

```{r}

source('010_data_preprocessing.R')
source("./functions.R")

library(here)
library(tidyverse)
library(magrittr)
library(tidyLPA)

library(ggplot2)
library(ggpubr)

library(mclust)
library(forcats)
library(hrbrthemes)

library(knitr)
library(kableExtra)

library(igraph)

```

```{r}

jobtitleanddescription = df_clean[, c("RecordNo", "Q18_1_open", "Q18a", "Occupation_DISCO", "Occupation")]

merged = merge(x = software_cleaned[!(software_cleaned$a2 %in% (software_aggregated %>% top_n(9, n) %$% a2)),], # throwing away top 9
                y = jobtitleanddescription,
                by = "RecordNo") %>%
  select(-a, -Q18_1_open, -Q18a, -Occupation_DISCO)

## merged %>% View


```


grouping devices per software for Software Projection

```{r}

# merged %>% group_by(a2, )


merged = merged %>%
  mutate(id = 1:nrow(merged)) %>% 
  group_by(a2, q) %>%
  mutate(QuantPerDevice = n()) %>% 
  spread(key = q, value = QuantPerDevice, fill = 0) %>% select(-id) %>%
  ungroup() %>% group_by(a2) %>% 
  mutate(stationaryQuantity = sum(Q4), # feature: quantity, software on desktop/laptop
         mobileQuantitiy = sum(Q5 + Q6), # feature: quantity, software on mobile/laptop devices
         cloudnessQuantity = sum(Q7)) %>% # feature: quantity, software is used on the web (cloud)
  select(-c(Q4, Q5,Q6, Q7))

merged$mobileBinary = ifelse(merged$mobileQuantitiy > 1, 1, 0) # feaure: whether software is principally used on several devices
merged$cloudnessBinary  = ifelse(merged$cloudnessQuantity > 1, 1, 0) # feature: whether software is principally possess web version

```

grouping device-based items and questionnaire items for Respondent's Projection

```{r}



```



The most simple scenario - just assume that there is no difference between devices. Use Respondent Id and Software Title as Ids. 

```{r}

g = graph.empty()

## TODO: fefactor assinging node and edge variables without unique repetition
## SOLVED: TRUE is for respondents, FALSE for software
g = add.vertices(g, nv = length(merged$RecordNo %>% unique()),
                 attr = list(name = paste0("A", merged$RecordNo %>% unique()),
                             occupation = merged[!duplicated(merged$RecordNo),]$Occupation,
                             type = rep(TRUE, length(merged$RecordNo %>% unique()))))


## SOLVED: checking order of names and attributes
## merged$a2 %>% unique()  %>% tail()
## merged[!duplicated(merged$a2),]$a2 %>% tail()

g = add.vertices(g, nv = length(merged$a2 %>% unique()),
                 attr = list(name = paste0("B", merged$a2 %>% unique()),
                             mobileBinary = merged[!duplicated(merged$a2),]$mobileBinary, ## assigning mobileBinary variable
                             cloudnessBinary = merged[!duplicated(merged$a2),]$cloudnessBinary,
                             stationaryQuantity = merged[!duplicated(merged$a2),]$stationaryQuantity,
                             mobileQuantity = merged[!duplicated(merged$a2),]$mobileQuantitiy,
                             cloudnessQuantity = merged[!duplicated(merged$a2),]$cloudnessQuantity,
                             type = rep(FALSE, length(merged$a2 %>% unique()))))


# we need to turn edgeList into a vector (and using names instead of indexes)
edgeListVec = as.vector(t(as.matrix(data.frame(S1 = paste0("A", merged$RecordNo),
                                               S2 = paste0("B", merged$a2)))))

g = add.edges(g, edgeListVec)

## is.bipartite(g)

```

Inspecting Software Projection, checking hypothesises

```{r}

proj = bipartite_projection(g)[[1]]

## INFO: 1 means zero - absence of feature, 2 - presence of feature
## types might be integers starting with 1, not obvious

V(proj)$mobileBinary[V(proj)$mobileBinary == 1] = 2
V(proj)$mobileBinary[V(proj)$mobileBinary == 0] = 1


V(proj)$cloudnessBinary[V(proj)$cloudnessBinary == 1] = 2
V(proj)$cloudnessBinary[V(proj)$cloudnessBinary == 0] = 1

## V(proj)$cloudnessBinary %>% as.factor() %>% summary()
## V(proj)$mobileBinary %>% as.factor() %>% summary()

assortativity.nominal(proj, types = V(proj)$mobileBinary)


## V(proj)$mobileBinary %>% hist()
## V(proj)$cloudnessBinary %>% hist()

assortativity.nominal(proj, types = V(proj)$cloudnessBinary)

## assort numeric
assortativity(proj, V(proj)$stationaryQuantity)
## FIXME: assortativity(proj, V(proj)$mobileQuantity)

assortativity(proj, V(proj)$cloudnessQuantity)

```

Inspecting Respondents Network

```{r}

proj = bipartite_projection(g)[[2]]

## INFO: 1 means zero - absence of feature, 2 - presence of feature
## types might be integers starting with 1, not obvious

V(proj)$occupation %>% unique()

tmp = 0
sapply(V(proj)$occupation %>% unique(), simplify = FALSE, USE.NAMES = FALSE,  function(x) {
  tmp <<- tmp + 1
  V(proj)$occupation[V(proj)$occupation == x] <<- tmp
})

V(proj)$occupation = as.integer(as.character(V(proj)$occupation))
V(proj)$occupation %>% class()

x = "Teaching"
tmp = 1
V(proj)$occupation[V(proj)$occupation == x] <- tmp

recode(V(proj)$occupation, "c(1,2,3,4,5)='Five or Less'")

V(proj)$mobileBinary[V(proj)$mobileBinary == 1] = 2
V(proj)$mobileBinary[V(proj)$mobileBinary == 0] = 1

## V(proj)$cloudnessBinary[V(proj)$cloudnessBinary == 1] = 2
## V(proj)$cloudnessBinary[V(proj)$cloudnessBinary == 0] = 1

assortativity.nominal(proj, types = V(proj)$occupation)


```



Exporting to Networkx

```{r}

write.graph(g, file = here("data/biGraph.graphml"), format = "graphml")

```
