```{r}

library(tidyverse)
library(magrittr)
library(tidyLPA)

library(mclust)
library(forcats)
library(hrbrthemes)

source("./functions.R")

```

Showing job shifts in connection with associated software is not possible due to NAs in Q21_1_open (previous job)
TODO: transition plots for jobs
TODO: transition plots for education

```{r}

df_clean$Q18_1_open %>% as.factor() %>% summary()
df_clean$Q21_1_open %>% as.factor() %>% summary()

df_clean$profile_education %>% summary

# Q18_1_open:Q18_a - job title + tasks description
# Q21_1_open:Q22 - previous job titles + tasks description

```

Here I am excluding timing columns


```{r}

df_clean %<>%
  dplyr::select(-c(page_pSC1_timing:tot_time))

# df_clean %>% nrow
na_vector = apply(df_clean, 2, function(x){

  sum(is.na(x))

})

na_vector[na_vector > 0] # which variables produce most of the NAs
df_final = df_clean %>% dplyr::select(
                                      names(na_vector[na_vector == 0]),
                                      -Occupation_Num, -status, -Occupation_DISCO,
                                      -c(Q85a_1_1, Q85a_2_1, Q85a_3_1, Q85a_4_1),
                                      -c(Q21_1_open, Q22),
                                      -c(Q18_1_open, Q18a),
                                      -c(comments, Q4, Q5, Q6, Q7))


df_final %>% nrow
df_final %>% ncol

```

Based on the info about NAs in the following chunk I updated columns.csv
UPD: not necessary right now 

```{r}

# FIXME: ?set not_mentioned?

# Q24 - what industry do you work in
# Q21 - what was your last (main) job titled
# Q23 Did you work in the public or private sector
# Q85_4_5: Mobile phone: other
# Q85_4_6: Mobile phone: Blackbery OS

# Less than 150 NAs:
# Q20 - what industry do you work in
# Q18 - what is your position/job title
# Q19 - do you work in a public/private sector


```

Reordering variables to make values semi-continuous


```{r}

df_final$Q9[df_final$Q9 == 4] = 0
df_final$Q10[df_final$Q10 == 4] = 0
df_final$Q11[df_final$Q11 == 4] = 0
df_final$Q12[df_final$Q12 == 4] = 0
df_final$Q13[df_final$Q13 == 4] = 0
df_final$Q14[df_final$Q14 == 4] = 0
df_final$Q15[df_final$Q15 == 4] = 0
df_final$Q16[df_final$Q16 == 4] = 0

df_final$Q17_R = 6 - df_final$Q17


```

Description of items for LPA

```{r}

# Q1 - language

# TODO: ask about numbers
# Q3_1 - Desktop
# Q3_2 - Laptop
# Q3_3 - Tablet
# Q3_4 - Mobile phone/Smartphone

#

# Q8_v2_1 - Built-in default settings
# Q8_v2_2 - Plugins/add-ons/extensions
# Q8_v2_3 - Script to extend Software
# Q8_v2_4 - I reprogram

# Traditional Surveys
# Q9 - Q10 - Q11 - Q12 - Q13 - Q14 - Q15 - Q16 - Q16

# Q17_R - employment status




```


LPA


 ```{r}

# Q17 - employment status, using Reversed Ordered Q17_R instead

vars_to_exclude = c("RecordNo", "weight","Q17",
                    "Occupation", "profile_education",
                    "profile_age2", "profile_age1",
                    "region", "Q1", "gender")

d = df_final

colnames_lpa = colnames(d)[!(colnames(d) %in% vars_to_exclude)]


```

Number of profiles to choose - analytically - less BIC is better

```{r}

fit_output = explore_model_fit(d %>% dplyr::select(colnames_lpa),
                               n_profiles_range = 1:6)


fit_output %>% View

```

Number of profiles to choose - visually

```{r}

to_plot = fit_output %>%
  gather(`Covariance matrix structure`, val, -n_profiles) %>% 
  mutate(`Covariance matrix structure` = as.factor(`Covariance matrix structure`),
         val = abs(val)) # this is to make the BIC values positive (to align with more common formula / interpretation of BIC)


to_plot$`Covariance matrix structure` = fct_relevel(to_plot$`Covariance matrix structure`,
                                                    "Constrained variance, fixed covariance",
                                                    "Freed variance, fixed covariance",
                                                    "Constrained variance, constrained covariance",
                                                    "Freed variance, freed covariance")

# Based on plot, either 3 or 4 profiles should be setted up

ggplot(to_plot,
       aes(x = n_profiles, y = val, color = `Covariance matrix structure`, group = `Covariance matrix structure`)) +
  geom_line() +
  geom_point() +
  ylab("BIC (smaller value is better)") +
  theme_ipsum_rc()


```

DONE: exclude binary variables from LPA

# OLD: Best on the BIC, we should choose EEE = Constrained variance, constrained covariance model = model 2


```{r}

m3 = estimate_profiles(d,
                       colnames_lpa,
                       n_profiles = 5, 
                       model = 2,
                       return_orig_df = T)


```


Plotting 


```{r}

# RColorBrewer::brewer.pal(n, pal)
# https://www.r-bloggers.com/how-to-expand-color-palette-with-ggplot-and-rcolorbrewer/

plot_profiles(m3[, !(colnames(m3) %in% vars_to_exclude)])


```
