---
title: "Untitled"
mainfont: DejaVu Sans
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
  html_document: default
  word_document: default
  font-family: Times New Roman
---

I am adding Q8v_2_* questions to MDS in this Script
Q4-Q7 are questions regarding soft on different devices


```{r}

# source(knitr::purl("1_.Rmd", output = tempfile(), documentation = 0))

source('010_data_preprocessing.R')

library(tidyverse)
library(magrittr)
library(tidyLPA)

library(ggplot2)
library(ggpubr)

library(mclust)
library(forcats)
library(hrbrthemes)

source("./functions.R")

```

Here I am excluding timing columns


```{r}

df_clean %<>%
  dplyr::select(-c(page_pSC1_timing:tot_time))

# df_clean %>% nrow
na_vector = apply(df_clean, 2, function(x){

  sum(is.na(x))

})

na_vector[na_vector > 0] # which variables produce most of the NAs
df_final = df_clean %>% dplyr::select(
                                      names(na_vector[na_vector == 0]),
                                      -Occupation_Num, -status, -Occupation_DISCO,
                                      -c(Q85a_1_1, Q85a_2_1, Q85a_3_1, Q85a_4_1),
                                      -c(Q21_1_open, Q22),
                                      -c(Q18_1_open, Q18a),
                                      -c(comments, Q4, Q5, Q6, Q7))


# df_final %>% nrow
# df_final %>% ncol

```

Based on the info about NAs in the following chunk I updated columns.csv
UPD: not necessary right now 

```{r}

# FIXME: ?set not_mentioned?

# Q24 - what industry do you work in
# Q21 - what was your last (main) job titled
# Q23 Did you work in the public or private sector
# Q85_4_5: Mobile phone: other
# Q85_4_6: Mobile phone: Blackbery OS

# Less than 150 NAs:
# Q20 - what industry do you work in
# Q18 - what is your position/job title
# Q19 - do you work in a public/private sector


```

Reordering variables to make values semi-continuous


```{r}

df_final$Q9[df_final$Q9 == 4] = 0
df_final$Q10[df_final$Q10 == 4] = 0
df_final$Q11[df_final$Q11 == 4] = 0
df_final$Q12[df_final$Q12 == 4] = 0
df_final$Q13[df_final$Q13 == 4] = 0
df_final$Q14[df_final$Q14 == 4] = 0
df_final$Q15[df_final$Q15 == 4] = 0
df_final$Q16[df_final$Q16 == 4] = 0

df_final$Q17_R = 6 - df_final$Q17


```

Description of items for LPA

```{r}

# Q1 - language

# TODO: ask about numbers
# Q3_1 - Desktop
# Q3_2 - Laptop
# Q3_3 - Tablet
# Q3_4 - Mobile phone/Smartphone
#

# Q8_v2_1 - Built-in defand problem-solving
# Q16 - updating IT skills


# Q17_R - employment 



```



Here I am filtering software out of the top 9

```{r}


jobtitleanddescription <- df_clean[, c("RecordNo", "Q18_1_open", "Q18a", "Occupation_DISCO", "Occupation")]


merged <- merge(x = software_cleaned[!(software_cleaned$a2 %in% (software_aggregated %>% top_n(9, n) %$% a2)),], # throwing away top 9
                y = jobtitleanddescription,
                by = "RecordNo") %>%
  select(-a, -Q18_1_open, -Q18a, -Occupation_DISCO)





```


TODO: remake the table with a `q` per `a2`
FIXME: what I was doing wrong before I have not excluded repeated items per respondent
# Fixing it


```{r}


merged_quas = merged[!is.na(merged$a2), ] %>% # removing NA's from the a column
  dplyr::rename(a = a2) %>% # FIXME: loosing the information about the device used
  select(-q)

merged_quas = merged_quas %>%
  group_by(RecordNo, a) %>%
  mutate(n = n()) %>% dplyr::filter(n < 2) %>% dplyr::select(-n) %>%
  ungroup() # moving out duplicates produced by Q4- and so on quesions


```

adding Q8 questions with quasi-ordinal scale

```{r}

# df_clean %>% colnames()

df_quas = df_clean %>% select(RecordNo, Q8_v2_1:Q16)

# anti_join(df_quas, merged_quas, by = "RecordNo") %>% View # 180 respondents are missing

df_merged_quas = inner_join(df_quas, merged_quas, by = "RecordNo")
# df_merged_quas %>% View


```

FIXME: think about how to adjust number of users  
UPD: simple decision might be just to throw away software which is used less than by 5 respondents in the sample  

```{r}

pre_dist_multi = df_merged_quas %>% select(-Occupation) %>% 
  group_by(a) %>% 
  mutate_at(vars(Q8_v2_1:Q16),
            funs("agr" = sum(.))) %>% mutate(n = n()) %>%
  mutate_at(vars(Q8_v2_1_agr:Q16_agr),
                   funs("norm" = . / n)) %>% 
  select(-c(Q8_v2_1_agr:Q16_agr),
         -c(Q8_v2_1:Q16))  %>%
  dplyr::rename(respondents_quant = n)  %>%
  filter(row_number() == 1)  %>%
  ungroup() %>%  arrange(desc(respondents_quant)) # %>% View


# pre_dist_multi$a %>% as.factor() %>% summary()
# pre_dist_multi %>% View


```

grouping is made for occupations

```{r}

pre_dist_occupations = df_merged_quas %>%
  gather(key, val, Occupation) %>% 
  dplyr::select(a, key, val) %>% 
  group_by(a, val) %>% tally() %>%
  spread(val, n, fill = 0)  %>%
  ungroup()


# pre_dist_occupations$a %>% as.factor() %>% summary()

```

joining all together

```{r}

pre_dist_multi_final = inner_join(pre_dist_multi, pre_dist_occupations, by = "a")


```

Generally, each software item transcends from the respondent. 

for each respondent we calculate the number of:  
 - platforms used  
 - OS used  
 - OS used per platform  
aggregate this per software item using mean() and treating them equally.  


```{r}

software_cleaned$RecordNo %>% unique() %>% length() # only 842 indicated the software they are using
dfDiversity$RecordNo %>% unique() %>% length()


df %>% filter(status == 1 & !is.na(Q85_1_1)) %>% nrow

# software_cleaned$q %>% as.factor() %>% summary()

software_cleaned = software_cleaned %>%
  select(-a) %>%
  dplyr::rename(a = a2)


dfDiversity = df_clean %>%
  select(RecordNo, Q85_1_1:Q85_4_5) %>%
  replace(is.na(.), 0)  %>%
  mutate(DesktopOsDiversity = rowSums(select(., contains("Q85_1_"))),
         LaptopOsDiversity = rowSums(select(., contains("Q85_2_"))),
         TabletOsDiversity = rowSums(select(., contains("Q85_3_"))),
         MobileOsDiversity = rowSums(select(., contains("Q85_4_"))))  %>%
  select(RecordNo, contains("Diversity"))

dfDiversity %>% filter(DesktopOsDiversity > 1) %>% nrow() # 49 respondents use more than one OS for desktop
dfDiversity %>% filter(LaptopOsDiversity > 1) %>% nrow() # 47 respondents use more than one OS for laptop
dfDiversity %>% filter(TabletOsDiversity > 1) %>% nrow() # 36 respondents use more than one OS for tablet
dfDiversity %>% filter(MobileOsDiversity > 1) %>% nrow() # 46 respondents use more than one OS for mobile

# Are they are the same respondents?

c(dfDiversity %>% filter(DesktopOsDiversity > 1) %$% RecordNo, dfDiversity %>% filter(LaptopOsDiversity > 1) %$% RecordNo,
  dfDiversity %>% filter(TabletOsDiversity > 1) %$% RecordNo, dfDiversity %>% filter(MobileOsDiversity > 1) %$% RecordNo) %>% unique() %>% length() # 81 respondents in total use more than 1 OS regarding all platforms

## library(dplyrExtras)
inner_join(software_cleaned, df_clean %>% select(RecordNo, Q85_1_1:Q85_4_5), by = "RecordNo") %>% # View
  mutate(g = ifelse(q == "Q4",
                    rowSums(select(., contains("Q85_1_"))),
                    NA)
         ) %>% View

  
##  mutate_if(q == "Q4", tst = rowSums(select(., contains("Q85_1_"))))


is.na(df_clean$Q85_1_1) %>% sum()
df_clean %>% nrow()

is.na(df_clean$Q85_3_1) %>% sum()

is.na(df_clean$Q3_1) %>% sum()
is.na(df_clean$Q3_2) %>% sum()


df_clean %>% nrow()

# anti_join(software_cleaned, dfDiversity, by = "RecordNo") %>% View
# inner_join(software_cleaned, dfDiversity, by = "RecordNo") %$% RecordNo %>% unique() %>% length()

```
exclude respondents who use multiple OS in order to uniquely attribute software items across devices and OS

```{r}


software_clean_unique = software_cleaned %>%
  filter(!(RecordNo %in% (c(dfDiversity %>% filter(DesktopOsDiversity > 1) %$% RecordNo,
                            dfDiversity %>% filter(LaptopOsDiversity > 1) %$% RecordNo,
                            dfDiversity %>% filter(TabletOsDiversity > 1) %$% RecordNo,
                            dfDiversity %>% filter(MobileOsDiversity > 1) %$% RecordNo) %>% unique())))

df_clean_unique = df_clean %>%
  filter(!(RecordNo %in% (c(dfDiversity %>% filter(DesktopOsDiversity > 1) %$% RecordNo,
                            dfDiversity %>% filter(LaptopOsDiversity > 1) %$% RecordNo,
                            dfDiversity %>% filter(TabletOsDiversity > 1) %$% RecordNo,
                            dfDiversity %>% filter(MobileOsDiversity > 1) %$% RecordNo) %>% unique())))




```


```{r}



inner_join(software_clean_unique, df_clean_unique %>% select(RecordNo, Q85_1_1:Q85_4_5),
           by = "RecordNo") %>% View


  mutate(g = ifelse(q == "Q4",
                    rowSums(select(., contains("Q85_1_"))),
                    NA)
         ) %>% View

  
##  mutate_if(q == "Q4", tst = rowSums(select(., contains("Q85_1_"))))



```


# Pre-MDS data preparation, scaling  

Scaling Before MDS, results are even worse    
UPD: scaling should be accomplished for all of the vars, another fix

```{r}

pre_dist_multi_final %>% colnames()

## scaling only for occupations since they represent absolute frequencies

pre_dist_multi_final[,-c(1:16)] %<>% apply(2, function(X) scale(X))


# pre_dist_multi_final[,-c(1:3)] %<>% apply(2, function(X) scale(X, center = FALSE))

pre_dist_multi_final %>% View
## pre_dist_multi_final$a %>% as.factor() %>% summary()

```

# MDS includes only survey items

"euclidean" 'maximum' 'manhattan' 'minkowski' 'canberra' 'binary'  
manhattan is good  
canberra - great division  


```{r}

p = flexible_clustering(pre_dist_multi_final, "canberra", 5, 12, 11)

ggsave(device="png", plot=p, filename="./plots/kmeans_canberra.png",
       scale=.2, height = 1024, width = 1024, units = "mm")

p

```
